---
title: "Validation with RFA"
author: "Iris Zhong"
date: "1/30/2022"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(readxl)
# library(readxlsb)
library(tidyverse)
```


```{r import data}
data_2020 <- read_excel(here("data/xlsx", "2020-21 Professional Personnel Individual Staff Report updated.xlsx")) %>% 
  mutate(PublicID = as.numeric(PublicID)) %>% 
  rename(YearsInEd = YearsInED) %>%
  mutate(AnnualSalary = ifelse(AnnualSalary == "Salary Excluded for Fictitious", NA, AnnualSalary))

data_2014 <- read_excel(here("data/xlsx", "2014-15 Professional Personnel Individual Staff Report.xlsx"))

data_2015 <- read_excel(here("data/xlsx", "2015-16 Professional Personnel Individual Staff Report.xlsx"))

data_2016 <- read_excel(here("data/xlsx", "2016-17 Professional Personnel Individual Staff Report.xlsx"))

data_2017 <- read_excel(here("data/xlsx", "2017-18 Professional Personnel Individual Staff Report.xlsx"))

data_2018 <- read_excel(here("data/xlsx", "2018-19 Professional Personnel Individual Staff Report.xlsx")) %>% rename(YearsInEd = YearsInED)

data_2019 <- read_excel(here("data/xlsx", "2019-20 Professional Personnel Individual Staff Report.xlsx")) %>% rename(YearsInEd = YearsInED)

```




```{r}
school_2019_rfa <- read_excel(here("data/xlsx", "Teachers-by-race_2019-20.xlsx")) %>%
  pull(`School Name`)
school_2018_rfa <- read_excel(here("data/xlsx", "Teachers-by-race_2018-19.xlsx")) %>%
  pull(`School Name`)
school_2017_rfa <- read_excel(here("data/xlsx", "Teachers-by-race_2017-18.xlsx")) %>%
  pull(`School Name`)
school_2016_rfa <- read_excel(here("data/xlsx", "Teachers-by-race_2016-17.xlsx")) %>%
  pull(`School Name`)
school_2015_rfa <- read_excel(here("data/xlsx", "Teachers-by-race_2015-16.xlsx")) %>%
  pull(`School Name`)
school_2014_rfa <- read_excel(here("data/xlsx", "Teachers-by-race_2014-15.xlsx")) %>%
  pull(`School Name`)

```

```{r}
rfa_2019 <- read_excel(here("data/xlsx", "Teachers-by-race_2019-20.xlsx")) %>% rename(school_name = `School Name`, teacher_n = `Teachers: Total`)
rfa_2018 <- read_excel(here("data/xlsx", "Teachers-by-race_2018-19.xlsx")) %>% rename(school_name = `School Name`, teacher_n = `Teachers: Total`)
rfa_2017 <- read_excel(here("data/xlsx", "Teachers-by-race_2017-18.xlsx")) %>% rename(school_name = `School Name`, teacher_n = `Teachers: Total`)
rfa_2016 <- read_excel(here("data/xlsx", "Teachers-by-race_2016-17.xlsx")) %>% rename(school_name = `School Name`, teacher_n = `Teachers: Total`)
rfa_2015 <- read_excel(here("data/xlsx", "Teachers-by-race_2015-16.xlsx")) %>% rename(school_name = `School Name`, teacher_n = `Teachers: Total`)
rfa_2014 <- read_excel(here("data/xlsx", "Teachers-by-race_2014-15.xlsx")) %>% rename(school_name = `School Name`, teacher_n = `Teachers: Total`)

```




RFA counting method:

> Teacher counts are the full-time equivalent (FTE) of teachers at every school.
For example, a teacher who worked 50% FTE (half-time) at two separate schools would be counted as ½ of a teacher (i.e., ½ FTE) at each of the two schools. 


# First try

only select classroom teachers, and use their FTE as percentages


```{r}
data_2014_teacher <- data_2014 %>% filter(CategoryDescription == "Classroom Teachers") 
data_2015_teacher <- data_2015 %>% filter(CategoryDescription == "Classroom Teachers") 
data_2016_teacher <- data_2016 %>% filter(`Category Description 2017-` == "Classroom Teachers")
data_2017_teacher <- data_2017 %>% filter(`Category Description 2017-` == "Classroom Teachers")
data_2018_teacher <- data_2018 %>% filter(`Category Description 2017-` == "Classroom Teachers")
data_2019_teacher <- data_2019 %>% filter(`Category Description 2017-` == "Classroom Teachers")
data_2020_teacher <- data_2020 %>% filter(`Category Description 2017-` == "Classroom Teachers")
```



```{r write clean function}
clean_data <- function(data) {
  
  data <- data %>% 
    mutate(FTE = as.numeric(`FTE%`)/100) %>%
    dplyr::select(SY, PublicID, FTE)
  
  return(data)
  
}
```


```{r}
data_list <- list(data_2014_teacher, data_2015_teacher, data_2016_teacher, data_2017_teacher, data_2018_teacher, data_2019_teacher, data_2020_teacher)

temp <- lapply(data_list, clean_data)
```

```{r}
teacher_n_summary<- sapply(temp, function(x){return(sum(x$FTE))})
```

```{r}
teacher_n_rfa <- c(116944, 116450, 118273, 118244, 119308, 119966, NA)
```

```{r}
year_list <- c("2014-15", "2015-16", "2016-17", "2017-18", "2018-19", "2019-20", "2020-21")
teacher_n_compare <- data.frame(year_list, teacher_n_summary, teacher_n_rfa) %>%
  pivot_longer(cols = c("teacher_n_summary", "teacher_n_rfa"), names_to = "source", values_to = "n")
```

```{r}
ggplot(teacher_n_compare, aes(x = year_list, y = n, color = source, group = source)) +
  geom_point() +
  geom_path() +
  geom_text(aes(label = n), vjust = 0.8, nudge_x = .2)
```

There's still some gap.

# Second try

only select full-time classroom teachers, use FTE as percentages

```{r}
data_2014_2 <- data_2014_teacher %>% filter(`FT/PT` == "full time") 
data_2015_2 <- data_2015_teacher %>% filter(`FT/PT` == "full time") 
data_2016_2 <- data_2016_teacher %>% filter(`FT/PT` == "full time")
data_2017_2 <- data_2017_teacher %>% filter(`FT/PT` == "full time")
data_2018_2 <- data_2018_teacher %>% filter(`FT/PT` == "full time")
data_2019_2 <- data_2019_teacher %>% filter(`FT/PT` == "full time")
data_2020_2 <- data_2020_teacher %>% filter(`FT/PT` == "full time")
```


```{r}
data_list_2 <- list(data_2014_2, data_2015_2, data_2016_2, data_2017_2, data_2018_2, data_2019_2, data_2020_2)
temp <- lapply(data_list_2, clean_data)
teacher_n_summary_2 <- sapply(temp, function(x){return(sum(x$FTE))})
```

```{r}
teacher_n_compare_2 <- data.frame(year_list, teacher_n_summary_2, teacher_n_rfa) %>%
  pivot_longer(cols = c("teacher_n_summary_2", "teacher_n_rfa"), names_to = "source", values_to = "n")
```


```{r}
ggplot(teacher_n_compare_2, aes(x = year_list, y = n, color = source, group = source)) +
  geom_point() +
  geom_path() +
  geom_text(aes(label = n), vjust = 0.8, nudge_x = .2)
```

Some uneven gaps.. 


# Third try

only select full-time classroom teachers, use FTE as percentages, remove teachers with less than 50 FTE

```{r}
data_2014_3 <- data_2014_2 %>% filter(as.numeric(`FTE%`) > 49) 
data_2015_3 <- data_2015_2 %>% filter(as.numeric(`FTE%`) > 49)
data_2016_3 <- data_2016_2 %>% filter(as.numeric(`FTE%`) > 49)
data_2017_3 <- data_2017_2 %>% filter(as.numeric(`FTE%`) > 49)
data_2018_3 <- data_2018_2 %>% filter(as.numeric(`FTE%`) > 49)
data_2019_3 <- data_2019_2 %>% filter(as.numeric(`FTE%`) > 49)
data_2020_3 <- data_2020_2 %>% filter(as.numeric(`FTE%`) > 49)
```

```{r}
data_list_3 <- list(data_2014_3, data_2015_3, data_2016_3, data_2017_3, data_2018_3, data_2019_3, data_2020_3)
temp <- lapply(data_list_3, clean_data)
teacher_n_summary_3 <- sapply(temp, function(x){return(sum(x$FTE))})
```

```{r}
teacher_n_compare_3 <- data.frame(year_list, teacher_n_summary_3, teacher_n_rfa) %>%
  pivot_longer(cols = c("teacher_n_summary_3", "teacher_n_rfa"), names_to = "source", values_to = "n")
```


```{r}
ggplot(teacher_n_compare_3, aes(x = year_list, y = n, color = source, group = source)) +
  geom_point() +
  geom_path() +
  geom_text(aes(label = n), vjust = 0.8, nudge_x = .2)
```

Nope!

# Fourth try

only select classroom teachers, exclude special ed


only select full-time classroom teachers, use FTE as percentages

```{r}
data_2014_4 <- data_2014_teacher %>% filter(!grepl("special ed",tolower(`PositionDescription`))) 
data_2015_4 <- data_2015_teacher %>% filter(!grepl("special ed",tolower(`PositionDescription`))) 
data_2016_4 <- data_2016_teacher %>% filter(!grepl("special ed",tolower(`Position Description 2017-`))) 
data_2017_4 <- data_2017_teacher %>% filter(!grepl("special ed",tolower(`Position Description 2017-`))) 
data_2018_4 <- data_2018_teacher %>% filter(!grepl("special ed",tolower(`Position Description 2017-`))) 
data_2019_4 <- data_2019_teacher %>% filter(!grepl("special ed",tolower(`Position Description 2017-`))) 
data_2020_4 <- data_2020_teacher %>% filter(!grepl("special ed",tolower(`Position Description 2017-`))) 
```


```{r}
data_list_4 <- list(data_2014_4, data_2015_4, data_2016_4, data_2017_4, data_2018_4, data_2019_4, data_2020_4)
temp <- lapply(data_list_4, clean_data)
teacher_n_summary_4 <- sapply(temp, function(x){return(sum(x$FTE))})
```

```{r}
teacher_n_compare_4 <- data.frame(year_list, teacher_n_summary_4, teacher_n_rfa) %>%
  pivot_longer(cols = c("teacher_n_summary_4", "teacher_n_rfa"), names_to = "source", values_to = "n")
```


```{r}
ggplot(teacher_n_compare_4, aes(x = year_list, y = n, color = source, group = source)) +
  geom_point() +
  geom_path() +
  geom_text(aes(label = n), vjust = 0.8, nudge_x = .2)
```

not right

# Fifth try

only count classroom teachers in charter school/school district, and use their FTE as percentages


```{r}
data_2014_5 <- data_2014_teacher %>% filter(LEATypeDescription %in% c("School District", "Charter School")) 
data_2015_5 <- data_2015_teacher %>% filter(LEATypeDescription %in% c("School District", "Charter School")) 
data_2016_5 <- data_2016_teacher %>% filter(LEATypeDescription %in% c("School District", "Charter School"))
data_2017_5 <- data_2017_teacher %>% filter(LEATypeDescription %in% c("School District", "Charter School"))
data_2018_5 <- data_2018_teacher %>% filter(LEATypeDescription %in% c("School District", "Charter School"))
data_2019_5 <- data_2019_teacher %>% filter(LEATypeDescription %in% c("School District", "Charter School"))
data_2020_5 <- data_2020_teacher %>% filter(LEATypeDescription %in% c("School District", "Charter School"))
```


```{r}
data_list_5 <- list(data_2014_5, data_2015_5, data_2016_5, data_2017_5, data_2018_5, data_2019_5, data_2020_5)
temp <- lapply(data_list_5, clean_data)
teacher_n_summary_5 <- sapply(temp, function(x){return(sum(x$FTE))})
```

```{r}
teacher_n_compare_5 <- data.frame(year_list, teacher_n_summary_5, teacher_n_rfa) %>%
  pivot_longer(cols = c("teacher_n_summary_5", "teacher_n_rfa"), names_to = "source", values_to = "n")
```


```{r}
ggplot(teacher_n_compare_5, aes(x = year_list, y = n, color = source, group = source)) +
  geom_point() +
  geom_path() +
  geom_text(aes(label = n), vjust = 0.8, nudge_x = .2)
```

numbers too small

# Sixth try


only count teachers in charter school/school district, and use their FTE as percentages

(include non-classroom teachers)


```{r}
data_2014_6 <- data_2014 %>% filter(LEATypeDescription %in% c("School District", "Charter School")) 
data_2015_6 <- data_2015 %>% filter(LEATypeDescription %in% c("School District", "Charter School")) 
data_2016_6 <- data_2016 %>% filter(LEATypeDescription %in% c("School District", "Charter School"))
data_2017_6 <- data_2017 %>% filter(LEATypeDescription %in% c("School District", "Charter School"))
data_2018_6 <- data_2018 %>% filter(LEATypeDescription %in% c("School District", "Charter School"))
data_2019_6 <- data_2019 %>% filter(LEATypeDescription %in% c("School District", "Charter School"))
data_2020_6 <- data_2020 %>% filter(LEATypeDescription %in% c("School District", "Charter School"))
```


```{r}
data_list_6 <- list(data_2014_6, data_2015_6, data_2016_6, data_2017_6, data_2018_6, data_2019_6, data_2020_6)
temp <- lapply(data_list_6, clean_data)
teacher_n_summary_6 <- sapply(temp, function(x){return(sum(x$FTE))})
```

```{r}
teacher_n_compare_6 <- data.frame(year_list, teacher_n_summary_6, teacher_n_rfa) %>%
  pivot_longer(cols = c("teacher_n_summary_6", "teacher_n_rfa"), names_to = "source", values_to = "n")
```


```{r}
ggplot(teacher_n_compare_6, aes(x = year_list, y = n, color = source, group = source)) +
  geom_point() +
  geom_path() +
  geom_text(aes(label = n), vjust = 0.8, nudge_x = .2)
```



# Some exploration


```{r}
school_2019_us <- data_2019 %>%
  group_by(LEAName, AUN,  School, SchNum) %>%
  
  #filter(!PublicID %in% fte_outlier_list) %>%
  #filter(`FT/PT` == "full time") %>%
  filter(`Category Description 2017-` == "Classroom Teachers") %>%
  #filter(EDFactsDescription != "KGTCH") %>%
  #filter(JobClass != "TPE" | is.na(JobClass) == T) %>% 
  filter(Status == "Active") %>%
  filter(!SchNum %in% c("9999", "Off-Site")) %>%
  summarize(n = sum(as.numeric(`FTE%`)/100)) %>%
  pull(School)
```

```{r}
Teachers_by_race_2019 <- read_excel("C:/Users/iris_/OneDrive - Stanford/Stanford/EDS seminar proj/Teachers-by-race_2019-20.xlsx")
school_2019_rfa <- Teachers_by_race_2019 %>% pull(`School Name`)
```

```{r}
setdiff(school_2019_us,school_2019_rfa)
setdiff(school_2019_rfa, school_2019_us)
```
`




```{r}
data_2017_teacher %>%
  #filter(`FT/PT` == "full time") %>%
  #filter(!PublicID %in% fte_outlier_list) %>%
  #filter(`CategoryDescription` == "Classroom Teachers") %>%
  filter(Status == "Active") %>%
  #filter(`EDF Category` != "KGTCH") %>%
  #filter(JobClass %in% c("PE","TPE","SP") | is.na(JobClass) == T) %>%
  filter(SchNum != "9999") %>%
  summarize(n = sum(as.numeric(`FTE%`)/100))
```

```{r}
data_2014 %>%
  group_by(PublicID) %>%
  summarize(fte = sum(as.numeric(`FTE%`)/100)) %>%
  arrange(desc(fte)) %>%
  filter(fte > 1)
```


# Seventh try

only select active classroom teachers, and use their FTE as percentages

```{r}
data_2014_7 <- data_2014_teacher %>% filter(Status == "Active") 
data_2015_7 <- data_2015_teacher %>% filter(Status == "Active") 
data_2016_7 <- data_2016_teacher %>% filter(Status == "Active")
data_2017_7 <- data_2017_teacher %>% filter(Status == "Active")
data_2018_7 <- data_2018_teacher %>% filter(Status == "Active")
data_2019_7 <- data_2019_teacher %>% filter(Status == "Active")
data_2020_7 <- data_2020_teacher %>% filter(Status == "Active")
```


```{r}
data_list_7 <- list(data_2014_7, data_2015_7, data_2016_7, data_2017_7, data_2018_7, data_2019_7, data_2020_7)
temp <- lapply(data_list_7, clean_data)
teacher_n_summary_7 <- sapply(temp, function(x){return(sum(x$FTE))})
```

```{r}
teacher_n_compare_7 <- data.frame(year_list, teacher_n_summary_7, teacher_n_rfa) %>%
  pivot_longer(cols = c("teacher_n_summary_7", "teacher_n_rfa"), names_to = "source", values_to = "n")
```


```{r}
ggplot(teacher_n_compare_7, aes(x = year_list, y = n, color = source, group = source)) +
  geom_point() +
  geom_path() +
  geom_text(aes(label = n), vjust = 0.8, nudge_x = .2)
```


# Eighth try

only select active classroom teachers (exclude schnum = "9999" off-site), and use their FTE as percentages

```{r}
data_2014_8 <- data_2014_7 %>% filter(!SchNum %in% c("9999", "Off-Site")) 
data_2015_8 <- data_2015_7 %>% filter(!SchNum %in% c("9999", "Off-Site"))  
data_2016_8 <- data_2016_7 %>% filter(!SchNum %in% c("9999", "Off-Site")) 
data_2017_8 <- data_2017_7 %>% filter(!SchNum %in% c("9999", "Off-Site")) 
data_2018_8 <- data_2018_7 %>% filter(!SchNum %in% c("9999", "Off-Site"))
data_2019_8 <- data_2019_7 %>% filter(!SchNum %in% c("9999", "Off-Site")) 
data_2020_8 <- data_2020_7 %>% filter(!SchNum %in% c("9999", "Off-Site")) 
```


```{r}
data_list_8 <- list(data_2014_8, data_2015_8, data_2016_8, data_2017_8, data_2018_8, data_2019_8, data_2020_8)
temp <- lapply(data_list_8, clean_data)
teacher_n_summary_8 <- sapply(temp, function(x){return(sum(x$FTE))})
```

```{r}
teacher_n_compare_8 <- data.frame(year_list, teacher_n_summary_8, teacher_n_rfa) %>%
  pivot_longer(cols = c("teacher_n_summary_8", "teacher_n_rfa"), names_to = "source", values_to = "n")
```


```{r}
ggplot(teacher_n_compare_8, aes(x = year_list, y = n, color = source, group = source)) +
  geom_point() +
  geom_path() +
  geom_text(aes(label = n), vjust = 0.8, nudge_x = .2)
```


# Nineth try

Same as eighth, but remove PublicID == "1880041809" or "-1629249266"

```{r}
data_2014_9 <- data_2014_8 %>% filter(!PublicID %in% c(1880041809,-1629249266))
data_2015_9 <- data_2015_8 %>% filter(!PublicID %in% c(1880041809,-1629249266))
data_2016_9 <- data_2016_8 %>% filter(!PublicID %in% c(1880041809,-1629249266))
data_2017_9 <- data_2017_8 %>% filter(!PublicID %in% c(1880041809,-1629249266))
data_2018_9 <- data_2018_8 %>% filter(!PublicID %in% c(1880041809,-1629249266))
data_2019_9 <- data_2019_8 %>% filter(!PublicID %in% c(1880041809,-1629249266))
data_2020_9 <- data_2020_8 %>% filter(!PublicID %in% c(1880041809,-1629249266))
```


```{r}
data_list_9 <- list(data_2014_9, data_2015_9, data_2016_9, data_2017_9, data_2018_9, data_2019_9, data_2020_9)
temp <- lapply(data_list_9, clean_data)
teacher_n_summary_9 <- sapply(temp, function(x){return(sum(x$FTE))})
```

```{r}
teacher_n_compare_9 <- data.frame(year_list, teacher_n_summary_9, teacher_n_rfa) %>%
  pivot_longer(cols = c("teacher_n_summary_9", "teacher_n_rfa"), names_to = "source", values_to = "n")
```


```{r}
ggplot(teacher_n_compare_9, aes(x = year_list, y = n, color = source, group = source)) +
  geom_point() +
  geom_path() +
  geom_text(aes(label = n), vjust = 0.8, nudge_x = .2)
```


# Check missing schools in nineth try

```{r}
setdiff(unique(data_2014_9 %>% pull(School)),school_2014_rfa)
setdiff(school_2014_rfa, unique(data_2014_9 %>% pull(School))) # 2014: two more schools in RFA

setdiff(unique(data_2015_9 %>% pull(School)),school_2015_rfa)
setdiff(school_2015_rfa, unique(data_2015_9 %>% pull(School)))

setdiff(unique(data_2016_9 %>% pull(School)),school_2016_rfa)
setdiff(school_2016_rfa, unique(data_2016_9 %>% pull(School)))

setdiff(unique(data_2017_9 %>% pull(School)),school_2017_rfa)
setdiff(school_2017_rfa, unique(data_2017_9 %>% pull(School))) # 2017: a lot of SDs as schools in RFA
```

```{r}
data_2020 %>% filter(SchNum == 9999)%>% filter(School != "Off-Site")
```




# Tenth try

```{r}
data_2014_10 <- data_2014_7 %>% filter(School != "Off-Site") %>% filter(!PublicID %in% c(1880041809,-1629249266))
data_2015_10 <- data_2015_7 %>% filter(School != "Off-Site") %>% filter(!PublicID %in% c(1880041809,-1629249266))
data_2016_10 <- data_2016_7 %>% filter(School != "Off-Site") %>% filter(!PublicID %in% c(1880041809,-1629249266))
data_2017_10 <- data_2017_7 %>% filter(School != "Off-Site") %>% filter(!PublicID %in% c(1880041809,-1629249266))
data_2018_10 <- data_2018_7 %>% filter(School != "Off-Site") %>% filter(!PublicID %in% c(1880041809,-1629249266))
data_2019_10 <- data_2019_7 %>% filter(School != "Off-Site") %>% filter(!PublicID %in% c(1880041809,-1629249266))
data_2020_10 <- data_2020_7 %>% filter(School != "Off-Site") %>% filter(!PublicID %in% c(1880041809,-1629249266))
```


```{r}
data_list_10 <- list(data_2014_10, data_2015_10, data_2016_10, data_2017_10, data_2018_10, data_2019_10, data_2020_10)
temp <- lapply(data_list_10, clean_data)
teacher_n_summary_10 <- sapply(temp, function(x){return(sum(x$FTE))})
```

```{r}
teacher_n_compare_10 <- data.frame(year_list, teacher_n_summary_10, teacher_n_rfa) %>%
  pivot_longer(cols = c("teacher_n_summary_10", "teacher_n_rfa"), names_to = "source", values_to = "n")
```


```{r}
ggplot(teacher_n_compare_10, aes(x = year_list, y = n, color = source, group = source)) +
  geom_point() +
  geom_path() +
  geom_text(aes(label = n), vjust = 0.8, nudge_x = .2)
```

```{r}
data_2014 %>% 
  filter(`CategoryDescription` == "Classroom Teachers") %>% 
  filter(Status == "Active") %>%
  #filter(!PublicID %in% c(1880041809,-1629249266)) %>%
  #filter(!SchNum %in% c("9999", "Off-Site"))  %>%
  summarize(sum_fte = sum(as.numeric(`FTE%`)/100))


data_2015 %>% 
  filter(`CategoryDescription` == "Classroom Teachers") %>% 
  filter(Status == "Active") %>%
  filter(!PublicID %in% c(1880041809,-1629249266)) %>%
  filter(!SchNum %in% c("9999", "Off-Site"))  %>%
  summarize(sum_fte = sum(as.numeric(`FTE%`)/100))

data_2017 %>% 
  filter(`Category Description 2017-` == "Classroom Teachers") %>% 
  #filter(`Primary Assignment` == "Yes") %>%
  filter(Status == "Active") %>%
  #filter(SchNum == "6162") %>% 
  filter(!PublicID %in% c(1880041809,-1629249266)) %>%
  #filter(!SchNum %in% c("9999", "Off-Site"))  %>%
  summarize(sum_fte = sum(as.numeric(`FTE%`)/100))
```


```{r}
data_2019_9 %>% 
  group_by(SchNum, School) %>%
  summarize(sum_fte = sum(as.numeric(`FTE%`)/100)) %>%
  full_join(rfa_2014, by = c("SchNum" = "School Number", "School" = "school_name")) %>%
  select(School, SchNum, sum_fte, teacher_n) %>%
  mutate(diff = round(sum_fte - teacher_n, 3)) %>%
  filter(diff != 0)
```

```{r}
data_2019 %>% filter(SchNum == "Off-Site")
```

